A Wide-Coverage Symbolic Natural Language Inference System

### 2019-03-04 paper2018/paper.tex
stergios_final

\paragraph{anaphora} Thanks to the above system, we can handle many
anaphoric cases, including E-Type and Donkey pronouns. Indeed, even
objects which have no syntactic representation can be added to the
environment. We follow here the general pattern outlined by
\citet{unger:2011}. However, we use a more general scope-extension
mechanism, which allows us to support examples like  the following:
\begin{lingex}
\item
    \label{ex:anaphora-scope}
\textbf{P1}	Every committee has a chairman.\\
\textbf{P2}	He is appointed its members.\\
\textbf{H} 	Every committee has a chairman appointed by members of the committee. \\ \textbf{Label:	YES} [FraCaS 122]
\end{lingex}
In the above example, the pronoun ``he'' is allowed to refer to the
object quantified over by ``every'', whose scope is extended
accordingly.

\paragraph{ellipsis} Ellipsis is handled in essentially the same way
as anaphora. This method is made especially straightforward thanks to
using GF syntax trees, which require an explicit argument for each
predicate. Thus, ellipsis are made explicit by the parsing phase. Such
ellptic expressions are handled in the same way as anaphora.
%
For example, in \ref{ex:acd}, the argument of ``did'' is
explicitly marked as an elliptic V2, which we resolve to ``speak'' in
that context.

\paragraph{definites} A naive way to handle definites is using an
existential type. However, if the semantics does not feature a
dynamic element, then the existential quantification is introduced
locally. This means that the quantifier can be introduced in the wrong
context. Consider the phrase ``everyone pets the dog''. The structure
of the interpretation would be
$\forall{} x. person(x) \to \exists{}y. dog(y) \wedge pet(x,y)$.
%
Instead, our take is that definites should be treated as an anaphoric
expression with an implicit referrent. That is, if the referent is not
found in the discourse, then it will be forcibly introduced, using an
existential type, \emph{at the top-level} of the expression. To be
able to do this, we record all definites without referent, using
another portion of the environment (using a monadic effect).
For the
above example, we obtain the desired interpretation:
$\exists{}y. dog(y) \wedge (\forall{}x. person(x) \to pet(x,y))$.

>>>>

\paragraph{Anaphora} Thanks to the above system, we can handle many
anaphoric cases, including E-Type and Donkey pronouns. Indeed, even
objects which have no syntactic representation can be added to the
environment. We follow here the general pattern outlined by
\citet{unger:2011}. However, we use a more general scope-extension
mechanism, which allows us to support examples like  the following:
\begin{lingex}
\item
    \label{ex:anaphora-scope}
\textbf{P1}	Every committee has a chairman.\\
\textbf{P2}	He is appointed its members.\\
\textbf{H} 	Every committee has a chairman appointed by members of the committee. \\ \textbf{Label:	YES} [FraCaS 122]
\end{lingex}
In the above example, the pronoun ``he'' is allowed to refer to the
object quantified over by ``every'', whose scope is extended
accordingly.

\paragraph{Ellipsis} Ellipsis is handled in essentially the same way
as anaphora. This method is made especially straightforward thanks to
using GF syntax trees, which require an explicit argument for each
predicate. Thus, ellipsis are made explicit by the parsing phase. Such
ellptic expressions are handled in the same way as anaphora.
%
For example, in \ref{ex:acd}, the argument of ``did'' is
explicitly marked as an elliptic V2, which we resolve to ``speak'' in
that context.

\paragraph{Definites} A naive way to handle definites is using an
existential type. However, if the semantics does not feature a
dynamic element, then the existential quantification is introduced
locally. This means that the quantifier can be introduced in the wrong
Context. Consider the phrase ``everyone pets the dog''. The structure
of the interpretation would be
$\forall{} x. person(x) \to \exists{}y. dog(y) \wedge pet(x,y)$.
%
Instead, our take is that definites should be treated as an anaphoric
expression with an implicit referrent. That is, if the referent is not
found in the discourse, then it will be forcibly introduced, using an
existential type, \emph{at the top-level} of the expression. To be
able to do this, we record all definites without referent, using
another portion of the environment (using a monadic effect).
For the
above example, we obtain the desired interpretation:
$\exists{}y. dog(y) \wedge (\forall{}x. person(x) \to pet(x,y))$.
